A Decentralized Pub/Sub System for Trusted Machine Economy

### 2020-04-28 paper.tex
Modify first paragraph of Introduction

\begin{IEEEkeywords}
publish/subscribe, decentralization, Distributed Ledger Technology
\end{IEEEkeywords}

\section{Introduction}
%TODO: cite examples
In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly, and such technologies can be widely used in various fields, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving}. As the physical and digital assets are deeply intertwined, the interactions among digital twins act as data exchanges.\cite{digitaltwin} With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is essential to build a secure, reliable and scalable data sharing services.

>>>>

\begin{IEEEkeywords}
Data Marketeplace, decentralization, Distributed Ledger Technology
\end{IEEEkeywords}

\section{Introduction}
%TODO: cite examples
In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings a potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving} and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. And data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform.
